### 2017-01-10 MSSM/MSSM.tex
Adding some more on categorisation to MSSM chapter

Parton showering and hadronisation are modelled using \texttt{PYTHIA 8} for all 
samples. Minimum--bias events generated with \texttt{PYTHIA 8} are
added to all \ac{MC} samples to model additional interactions.

@@

\subsection{Categorisation}
\label{sec:mssm_eventsel_categories}
As the analysis targets both the gluon--gluon fusion
and the b--associated production modes of MSSM Higgs
bosons, two exclusive categories are defined based on the 
number of b--tagged jets, where a jet is considered b--tagged
if it passes the medium working point of the \ac{CSV}v2 discriminator. 
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal
\item \textbf{b-tag}: At least 1 b--tagged jet and at most 1 
jet with \pT$>30$ GeV. Due to the different phase space considered for
b--tagging than for normal jet reconstruction this requirement does not necessarily
mean there will be only one jet in the event. The requirement reduces the sizeable \ttbar
background
\end{itemize}

Figure \ref{fig:mssm_cats_tt}a shows the number of jets 
in the \tautau channel, with \ref{fig:mssm_cats_tt}b showing
the number of b--tagged jets in that channel. The gluon--gluon fusion
signal and bb associated signal are overlaid on these distributions,
thus indicating the signal--sensitive bins, motivating the choice of categories.

\begin{figure}[h!]
\begin{center}
\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_tt_2016_log.png}}
\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_tt_2016_log.png}}
\end{center}
\caption{(a) Number of jets and (b) number of b--tagged jets in the \tautau channel. The gluon--gluon fusion signal (COLOUR)
and bb--associated signal (COLOUR2) are overlaid on the distribution, motivating the choice of
categorisation to target the two different signals. FIXME REMAKE THESE PLOTS WITH SIGNAL ON!}
\label{fig:mssm_cats_tt}
\end{figure}

\section{\ac{MC} to data correction factors}
\label{sec:mssm_mccorrs}
\subsubsection*{Tracking efficiency}
\subsubsection*{Electron, muon and tau ID and isolation}
\subsubsection*{Trigger efficiency}
\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ fake rate and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
\subsubsection*{\MET recoil corrections}
\subsubsection*{Top-quark \pT reweighting}
\subsubsection*{Drell-Yan shape reweighting}

@@

The use of the method presented relies on knowledge of $R_{W}^{OS/SS}$,
$R_{QCD}^{OS/SS}$, and on these two ratios not being too similar to each other. 
The ratio $R_{QCD}^{OS/SS}$ is measured in an anti--isolated
control region in data; this is described in section ADD REF. $R_{W}^{OS/SS}$ is 
taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{QCD}^{OS/SS}$
is close to 1.

@@

\item \Wjets:
\item QCD:

@@

@@

Figure \ref{fig:mssm_hmssm_2016} shows the expected (dashed line and grey bands)
and observed (blue shaded area bounded by solid line) exclusion of the search
presented in this chapter in the \mA-\tanb~ plane of the hMSSM scenario. 
MENTION FEATURE

>>>>

Parton showering and hadronisation are modelled using \texttt{PYTHIA 8} for all 
samples. Minimum--bias events generated with \texttt{PYTHIA 8} are
added to all \ac{MC} samples to model additional interactions. A reweighting
is then applied to the \ac{MC} samples to make the pile--up distribution match
that observed in data.

@@

\subsection{Categorisation}
\label{sec:mssm_eventsel_categories}
As the analysis targets both the gluon--gluon fusion
and the b--associated production modes of MSSM Higgs
bosons, two exclusive categories are defined based on the 
number of b--tagged jets, where a jet is considered b--tagged
if it passes the medium working point of the \ac{CSV}v2 discriminator. 
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item \textbf{No b-tag}: 0 b--tagged jets. This category targets the gg$\phi$ production mode but is also sensitive to some of the bb$\phi$ signal
\item \textbf{b-tag}: At least 1 b--tagged jet and at most 1 
jet with \pT$>30$ GeV. Due to the different phase space considered for
b--tagging than for normal jet reconstruction this requirement does not necessarily
mean there will be only one b--tagged jet in the event. The requirement reduces the sizeable \ttbar
background
\end{itemize}

Figure \ref{fig:mssm_cats_mt}a shows the number of jets 
in the \mutau channel, with \ref{fig:mssm_cats_mt}b showing
the number of b--tagged jets in that channel. The gluon--gluon fusion
signal and bb associated signal are overlaid on these distributions, normalised
to 100 times their cross--section times branching ratio at \mA=1 TeV and 
\tanb=50 in the $m_{\text{h}}^{\text{mod+}}$ scenario. From the distribution of the
gluon--gluon fusion signal in figure \ref{fig:mssm_cats_mt}b we can 
see that the vast majority of these signal events do not have any b-tagged jets, which
motivates the choice of the no b-tag category to target this signal. From
the bb associated signal in the same figure we also see that the majority of bb associated
signal events do not have any b-tagged jets either: either the b-jets in these events 
are too soft, or they do not pass the b-tagging requirements. This means the no b-tag 
category is also sensitive to some of the bb$\phi$ signal. The other observation we 
can make from the bb$\phi$ signal in figure \ref{fig:mssm_cats_mt}b is that there is not
such a large proportion of events with more than 1 b-tagged jet. From figure \ref{fig:mssm_cats_mt}a
we see that the \ttbar background starts to become more sizeable for events with more than
one jet. The definition of the b-tag category is therefore chosen with the inclusion
of the jet veto, such that the region where the \ttbar background becomes larger is excluded, 
while retaining a large proportion of the bb$\phi$ signal.

\begin{figure}[h!]
\begin{center}
\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
\end{center}
\caption{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon--gluon fusion signal (dashed
blue line) and bb--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
are normalised to 100 times their cross--section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$
scenario. We can see how the signal--sensitive bins motivate the choice of categories.}
\label{fig:mssm_cats_mt}
\end{figure}

\section{\ac{MC} to data correction factors}
\label{sec:mssm_mccorrs}
Because \ac{MC} samples are used for the signal predication, and 
to estimate some of the backgrounds, it is important to correct for possible 
mis-modelling with respect to the data. Dedicated control regions in
data are used to derive the \ac{MC} to data correction factors
that are applied to the \ac{MC} samples.
\subsubsection*{Tracking efficiency}
A discrepancy between the track reconstruction efficiency
in data and \ac{MC} for electrons and muons was found. $\eta$--dependent
scale factors are applied to mitigate the issue \cite{CMS-PAS-HIG-16-037}.
\subsubsection*{Electron, muon and tau ID and isolation}
Identification and isolation efficiencies in data and \ac{MC} are measured
for electrons, muons and hadronic taus. A tag--and--probe
method using \Zeenog (\Zmmnog) events is used to measure
the efficiencies for electrons (muons). The hadronic tau identification
and isolation efficiency is measured using a tag--and--probe method
making use of $Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
The measured efficiencies are used to construct scale factors to be
applied to the \ac{MC} samples as $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.
\subsubsection*{Trigger efficiency}
The electron, muon and hadronic tau trigger efficiencies are also measured
using tag--and--probe methods with the types of events as described for the identification
and isolation efficiencies. Because no trigger simulation is applied to
the \ac{MC} samples, the efficiency $\epsilon_{\text{Data}}$ is simply applied
to the \ac{MC} events. Because two electron/muon cross--triggers are 
used to select events in the \emu channel, the efficiencies of the different
cross trigger legs need to be combined. With one of the cross triggers having a
\pT~cut of 23 GeV on the muon leg and 12 GeV on the electron leg, and the
other having a minimum \pT~ of 23 GeV on the electron leg and 8 GeV on the muon
leg, the combined efficiency of the two triggers becomes:
\begin{equation}\label{eqn:mssm_em_trigeff}
\epsilon_{\text{data}} = \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele12}) + \epsilon_{\text{data}}(\text{Mu8})\cdot\epsilon_{\text{data}}(\text{Ele23}) - \epsilon_{\text{data}}(\text{Mu23})\cdot\epsilon_{\text{data}}(\text{Ele23}).
\end{equation}
\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ fake rate and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
The $\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rates
after applying the anti--electron and anti--muon discriminators are measured
using a tag--and--probe method with \Zeenog and \Zmmnog events. A scale
factor, to be applied to \ac{MC} events where the tau is faked by an electron or muon,
is derived as the ratio between the fake rate in data and the fake rate in \ac{MC} events.
\subsubsection*{\MET recoil corrections}
Differences in \MET~ resolution and response between data and \ac{MC} 
are accounted for by the application of recoil corrections
to signal, \Wjets and \Ztautau events. These corrections
are detailed in section \ref{sec:objects_met_recoilcorr}.
To correct for the difference in b--tagging efficiency
and light jet mis--tagging rates between data and \ac{MC}
\pT~ and $\eta$ dependent scale factors are derived as 
described in reference \cite{cms-btag-run2}. They 
are applied using the promote--demote method
as outlined in equation \ref{eqn:promotedemote}.
\subsubsection*{Top-quark \pT reweighting}
A reweighting which was derived during \ac{LHC} Run-1
to better match the top quark \pT~distribution in \ac{MC}
to that observed in data is applied to \ttbar events. Despite
the fact that the correction was derived during Run-1, it still
improves the data/\ac{MC} agreement in a \ttbar enriched
control region, as shown in figure \ref{fig:mssm_corrs_toppt}.
\begin{figure}[h!]
\begin{center}
\subfloat[Without top quark \pT~ reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016_notopptrwt.png}}
\subfloat[With top quark \pT~ reweighting]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}}
\end{center}
\label{fig:mssm_corrs_toppt}
\caption{\mTtot~ distribution in the \ttbar enriched control region
 (a) without and (b) with top quark \pT~ reweighting. The uncertainty band includes
the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty. We can see
that the data/\ac{MC} agreement in this control region improves when applying the top quark \pT~
reweighting, particularly in the high \mTtot~ tail.}
\end{figure}
\subsubsection*{Drell-Yan shape reweighting}
As the \ac{MC} samples used for the \Ztautau estimate
do not model the data well for events with high di-lepton
mass and high Z \pT~, a reweighting is applied to correct for this.
These weights are derived in bins of $\PZ/Pphoton*$ mass and \pT~
using \Zmm events in data, in such a way that they do not
change the overall Drell-Yan normalisation. The weights
are then applied to the \Ztautau and \Zellell background processes.

@@

The use of the method presented relies on knowledge of $R_{W}^{OS/SS}$,
$R_{QCD}^{OS/SS}$, and on these two ratios not being too similar to each other. 
The ratio $R_{QCD}^{OS/SS}$ is measured in an anti--isolated
control region in data; this is described in section \ref{sec:mssm_bkgs_etmt_qcdosss}. $R_{W}^{OS/SS}$ is 
taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{QCD}^{OS/SS}$
is close to 1.

@@

\item \Wjets: FIXME
\item QCD: FIXME

@@

FIXME

@@

Figure \ref{fig:mssm_hmssm_2016} shows the expected (dashed line and grey bands)
and observed (blue shaded area bounded by solid line) exclusion of the search
presented in this chapter in the \mA-\tanb~ plane of the hMSSM scenario. 
We should note again that this model, although defined for \tanb~ values
upwards of 10, is only strictly valid for \tanb~ below 10.
The small excluded area around \mA=200 GeV is genuine. It is caused by the 
production cross-section times branching ratio in the model, which is driven by
two effects \cite{CMS-PAS-HIG-16-007}. On the one hand the branching ratio into taus decreases with decreasing
\tanb~, while on the other hand a negative top--bottom interference effect increases the
gluon--gluon fusion cross-section with decreasing \tanb~. Therefore the
combined cross--section times branching ratio decreases with decreasing \tanb, until it
increases again from a low value of \tanb~ down to \tanb=1. The feature is 
thus expected to grow with more data.
